The \dealii{} Library, Version 8.5

### 2017-03-23 8.5/paper.tex
Update number of changes.
Add further points on changes to step-44 tutorial.
Also, fix and add to code-gallery example description

  \item More than 230 other features and bugfixes.
\end{itemize}
The more important ones of these changes will be detailed in the
following section.  Information on how to cite \dealii{} is provided
in Section \ref{sec:cite}.

@@

The updated step-44 tutorial program demonstrates the
use of the physical module in the context of a solid mechanics problem.

@@

In addition to tutorials, \dealii{} has a separate ``code gallery'' that
consists of programs shared by users as examples of what can be
done with \dealii{}. While not part of the release process, it is nonetheless
worth mentioning that the set of new programs since the last release covers
the following topics:
\marginpar{Add the muscle elasticity example if it is merged in time.}
  \begin{itemize}
    \item Auasi-static visco-elastic material behavior;
    \item Multiphase Navier-Stokes flow;
    \item The evolution of global-scale topography on planetary bodies;
    \item Goal-oriented elastoplasticity.
  \end{itemize}

>>>>

  \item More than 240 other features and bugfixes.
\end{itemize}
The more important ones of these changes will be detailed in the
following section.  Information on how to cite \dealii{} is provided
in Section \ref{sec:cite}.

@@

The updated step-44 tutorial program demonstrates the
use of the physics module in the context of a solid mechanics problem.
Additional updates to this tutorial include application of the new 
\texttt{CellDataStorage} class to store and retrieve local quadrature point 
data. An alternative approach to solving the linear system, previously 
performed by global static condensation of two of the three field variables, 
has been implemented using the \texttt{LinearOperator} class.

@@

In addition to tutorials, \dealii{} has a separate ``code gallery'' that
consists of programs shared by users as examples of what can be
done with \dealii{}. While not part of the release process, it is nonetheless
worth mentioning that the set of new programs since the last release covers
the following topics:
\marginpar{Add the muscle elasticity example if it is merged in time.}
  \begin{itemize}
    \item Quasi-static quasi-incompressible visco-elastic material behavior;
    \item Multiphase Navier-Stokes flow;
    \item The evolution of global-scale topography on planetary bodies;
    \item Goal-oriented elastoplasticity.
  \end{itemize}
